---
title: "Correlate Search Structure Document"
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Search Parameters and Justification

The search parameters for the literature search for the environmental correlates for 
dreissenid mussels are as follows:

> (mussel* AND (dreissen* OR zebra OR quagga) AND (invas* OR non-native OR introduc*))
> AND (habitat OR environment* OR niche) AND (suitability OR requirement* OR limit*)

This query was designed to capture both species of interest ( _Dreissena polymorpha_ and
_Dreissena rostriformis bugensis_), as well as potential synonyms for invasion. The second line
of the query as presented here functions to capture papers that evaluate the habitat of 
dreissenid mussels and their potential suitability for their establishment and persistence.

## Search Structure and Databases

```{r echo = FALSE}

## install.packages('webshot')
## webshot::install_phantomjs()

# Above packages may need to be install to run DiagrammeR code below.

library('DiagrammeR')

grViz("digraph flowchart {
  node [fontname = Helvetica, shape =  rectangle, fontsize = 12, 
       style = filled]
 
  tab1 [label = '@@1', fillcolor = LightSteelBlue, alpha = 0.5]
  tab2 [label = '@@2', fillcolor = LightBlue1]
  tab3 [label = '@@3', fillcolor = PaleTurquoise1]
  tab4 [label = '@@4', fillcolor = PaleTurquoise2]
  tab5 [label = '@@5', fillcolor = LightBlue2]
  tab6 [label = '@@6', fillcolor = PaleTurquoise3]
  tab7 [label = '@@7', fillcolor = LightBlue3]
  tab8 [label = '@@8', fillcolor = Honeydew2]
  tab9 [label = '@@9', fillcolor = Honeydew3]
  tab10 [label = '@@10', fillcolor = DarkSeaGreen3]
  
  tab1 -> tab2 [arrowhead = vee];
  tab1 -> tab3 [arrowhead = vee];
  
  tab3 -> tab4 [arrowhead = vee];
  tab4 -> tab6 [arrowhead = vee];
  tab6 -> tab8 [arrowhead = vee];
  
  tab2 -> tab5 [arrowhead = vee];
  tab5 -> tab7 [arrowhead = vee];
  tab7 -> tab8 [arrowhead = vee];
  
  tab8 -> tab9 [arrowhead = vee];
  tab9 -> tab10 [arrowhead = vee];
  
  }

  [1]: 'Query Databases'
  [2]: 'ASFA'
  [3]: 'Web of Science'
  [4]: 'Screen Records by Title'
  [5]: 'Screen Records by Title'
  [6]: 'Screen Records by Abstract'
  [7]: 'Screen Records by Abstract'
  [8]: 'Combine Database Records'
  [9]: 'Screen for Duplicates'
  [10]: 'Export for Analysis'
  
  ")

```

The above review process will be used for both parallel literature searches. Papers
will be retrieved from .bib files extracted from each database and analyzed using the 
'revtools' package. Titles will first be screened by title and then abstract using the 
following criteria:

> [1.] Zebra/quagga mussels topic of exploration?     Y/N, yes include

> [2.] North American range?                          North American included

> [3.] Observational, modeling or experimental?       Observational included

> [4.] Does it discuss correlates of distribution?    Y/N, yes included

Each paper will be evaluated against the above criteria in sequential order -
a failure to meet any of the criteria will result in an exclusion from the search. 
Failure to meet the search criteria as well as which criteria were failed will be
noted in each paper's entry in the analysis files for transparency.